Corticosteroids in HELLP syndrome

### 2023-10-28 data/synthesis copy.Rmd
Update

---
title: "Corticosteroids in HELLP syndrome"
subtitle: Data and synthesis script
date: "2023-09-26"
output: html_document
always_allow_html: yes
---

@@

@@

```{r}
subgr = update.meta(bin,subgroup = factor) 
forest.meta(subgr,pooled.events = T,xlim = c(.01,100), label.e = "Corticosteroids",label.c = "Placebo",just = "left", test.overall.common = T,colgap.left = ".5cm",col.subgroup = "black", fontsize = 7)
```

>>>>

---
title: "Corticosteroids in HELLP syndrome"
subtitle: Data and synthesis script
date: "2023-09-26"
output:
  html_document:
    df_print: paged
always_allow_html: yes
---

@@

\newpage

@@

```{r}
subgr = update.meta(bin,subgroup = factor) 
forest.meta(subgr,pooled.events = T,xlim = c(.01,100), label.e = "Corticosteroids",label.c = "Placebo",just = "left", test.overall.common = T,colgap.left = ".5cm",col.subgroup = "black", fontsize = 7 )
```

\newpage
